A Large-Scale Study of the Use of Eval in R

### 2020-08-21 inst/paper/main.tex
tpyo
Syntax highlighting for R

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\newcommand{\missingNumber}{\textcolor{red}{XX}\xspace}
\newcommand{\missingPercentage}{\textcolor{red}{XX\%}\xspace}
\newcommand{\missingTable}{\textcolor{red}{XXTable}\xspace}
\newcommand{\missingGraph}{\textcolor{red}{XXGraph}\xspace}
\usepackage{xcolor,xspace}
\begin{document}

\title{A Large-Scale Study of the Use of Eval in R}
\author{\vspace{-.8cm}\IEEEauthorblockN{\it\Large The Eval that Data Scientist Do}%
  %\IEEEauthorblockA{ dept} \\ \and
}  
\maketitle

@@

There are four different kinds of \c{eval} in the \emph{base} package:  \c{eval}, \c{evalq}, \c{eval.parent},  \c{local}.
The most important one is \c{eval}:

- the four eval functions in base
- the arguments, expr and envir, enclos
- which expressions are evaluated, which ones are left unchanged

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{listings}
\newcommand{\missingNumber}{\textcolor{red}{XX}\xspace}
\newcommand{\missingPercentage}{\textcolor{red}{XX\%}\xspace}
\newcommand{\missingTable}{\textcolor{red}{XXTable}\xspace}
\newcommand{\missingGraph}{\textcolor{red}{XXGraph}\xspace}
\usepackage[usenames,dvipsnames]{xcolor} 
\usepackage{xspace}

\lstset{ 
	language=R,                     % the language of the code
	basicstyle=\tiny\ttfamily, % the size of the fonts that are used for the code
	numbers=left,                   % where to put the line-numbers
	numberstyle=\tiny\color{Blue},  % the style that is used for the line-numbers
	stepnumber=1,                   % the step between two line-numbers. If it is 1, each line
	% will be numbered
	numbersep=5pt,                  % how far the line-numbers are from the code
	backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
	showspaces=false,               % show spaces adding particular underscores
	showstringspaces=false,         % underline spaces within strings
	showtabs=false,                 % show tabs within strings adding particular underscores
	%frame=single,                   % adds a frame around the code
	rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
	tabsize=2,                      % sets default tabsize to 2 spaces
	captionpos=b,                   % sets the caption-position to bottom
	breaklines=true,                % sets automatic line breaking
	breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
	keywordstyle=\color{RoyalBlue},      % keyword style
	commentstyle=\color{YellowGreen},   % comment style
	stringstyle=\color{ForestGreen}      % string literal style
} 
\begin{document}

\title{A Large-Scale Study of the Use of Eval in R}
\author{\vspace{-.8cm}\IEEEauthorblockN{
    \it\Large The Eval that Data Scientists Do}%
  %\IEEEauthorblockA{ dept} \\ \and
}  
\maketitle

@@

There are four different kinds of \c{eval} in the \emph{base} package:  \c{eval}, \c{evalq}, \c{eval.parent},  \c{local}.
The most important one is \c{eval}: \lstinline|eval(expr, envir, enclos)|

- the four eval functions in base

- the arguments, expr and envir, enclos

- which expressions are evaluated, which ones are left unchanged
